draft_final_assignment

### 2022-11-28 draft_final_assingment.Rmd
r_updates

```{r }
library(tidyverse)
library(quanteda)
library(quanteda.textstats)
library(readr)
library(dplyr)
library(quanteda.textplots)
library(uwot)
library(topicmodels)
library(tidytext)
library(ggrepel)
library(vader)
Library(tidyr)
```

@@

```{r}
df %>%
  is.na(summary)

sentiments <- vader_df(df$summary)

summary_sentiment <- cbind(df, select(sentiments,-text))

pos <- summary_sentiment %>% 
  arrange(desc(compound)) %>% 
  head()

for( i in rownames(pos) ) { 
  print(pos[i, "text"]) 
  print(pos[i, "compound"])
}

neg <- summary_sentiment %>% 
  arrange(compound) %>% 
  head()

for( i in rownames(neg) ) { 
  print(neg[i, "text"]) 
  print(neg[i, "compound"])
}
```

```{r}
library(tidyr)
#tweet_sentiment$date <- as.Date(tweet_sentiment$created)

wide_sentiment <- summary_sentiment %>%
  group_by(partisan, date) %>%
  summarise(score = mean(compound)) %>% 
  pivot_wider(names_from = partisan, values_from = score)

@@

ggplot(daily_sentiment, aes(date, colour=partisan)) +
  geom_point(aes(y=score),size=0.5) + geom_line(aes(y=score7))
```

>>>>

```{r }
library(tidyverse)
library(quanteda)
library(quanteda.textstats)
library(readr)
library(dplyr)
library(quanteda.textplots)
library(uwot)
library(topicmodels)
library(tidytext)
library(ggrepel)
library(vader)
library(tidyr)
```

@@

```{r}
#Loading df with VADER compount scores

summary_sentiment <- read_csv("https://raw.githubusercontent.com/juka19/tad_assignment3/main/data/data_w_vader.csv")
```

```{r}
library(tidyr)
#tweet_sentiment$date <- as.Date(tweet_sentiment$created) 
summary_sentiment <- summary_sentiment %>%
  mutate(partisan = ifelse(cosponsor_D_perc > 0.5,"Dem", 
                       ifelse(cosponsor_D_perc < 0.5,"Rep",
                              ifelse(cosponsor_D_perc == 0.5,"Neutral", NA))))

wide_sentiment <- summary_sentiment %>%
  group_by(partisan, date) %>%
  summarise(score = mean(compound)) %>% 
  pivot_wider(names_from = partisan, values_from = score) %>%
  select(-c("Neutral", "NA"))

@@

ggplot(daily_sentiment, aes(date, colour=partisan)) +
  geom_point(aes(y=score), size=0.5) + 
  geom_line(aes(y=score7)) + theme_minimal()
```
